---
title: "DATA 607, Group 4 : What are top Data Science skills? (Consolidated Analysis)"
author: "JM"
date: "March 26, 2017"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango
    code_folding: hide
---
## Consolidated Analysis
```{r eval=FALSE}
install.packages("rmarkdown") # Make cool dynamic documents
install.packages("knitr") # Run R Code Chunks
install.packages("ggplot2") # For plotting
install.packages("DT") # Interactive HTML tables
install.packages("tidyverse") # Tidy Universe
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(dplyr)
library(ggplot2)
library(maps)
library(mapdata)
library(knitr)
library("rmarkdown") 
library("DT") 
```

### Read Consolidated Data from our Repository
```{r}
ConsData <- read.csv("https://raw.githubusercontent.com/DATA607/Project3/master/dataframe.csv", stringsAsFactors = FALSE)
# Some Filtering of Data - C++ and Analytics as the data against these is spurious
ConsData <- ConsData %>% filter(skill != 'C++') %>% filter(skill != '(C++)') %>% filter(skill != 'analytics') %>% filter(skill != 'Analytics')
ConsData$count <- as.integer(ConsData$count)
```
```{r}
datatable(head(ConsData,3))
```


#### A sample of where our data comes from 
```{r}

RecordCounts <- ConsData %>% group_by(location) %>% summarise(Number=n()) 
datatable(RecordCounts)
```


### What are Top Skills

#### We are checking what are top sub-skills which data scientists. Later on we would look at Groupings of Skills.
```{r}
TopSkillsData <- ConsData %>% group_by(skill)  %>% summarise(Count=sum(count)) %>% arrange(desc(Count))

datatable(TopSkillsData)
```


#### A chart to represent the skills
```{r}

TopSkillsData <- head(TopSkillsData, 10)
TopSkillsData <- TopSkillsData %>% arrange(Count)
barplot(TopSkillsData$Count, main="Top 10 Skills", horiz=TRUE,
  names.arg=TopSkillsData$skill, las=1, cex.axis = 0.5, cex.names=0.5)

```


### What are Top Skills Groups
#### Download the Skill Groups Meta File
```{r}
SkillGroups <- read.csv("https://raw.githubusercontent.com/DATA607/Project3/master/SkillGroupings.txt", stringsAsFactors = FALSE, header = FALSE)
colnames(SkillGroups) <- c("Skill", "Group")
datatable(SkillGroups)
```


#### Join with Skill Counts data
##### C++ and analytics are spurious data for us, so these would be removed.
```{r}
TopSkillsGroupData <- ConsData %>% group_by(skill)  %>% summarise(Count=sum(count)) %>% arrange(desc(Count))

TopSkillsGroupData <- inner_join(TopSkillsGroupData, SkillGroups, by=c("skill" = "Skill"))
TopSkillsGroupData <- TopSkillsGroupData %>% group_by(Group) %>% summarise(GroupedCount=sum(Count)) %>% arrange(desc(GroupedCount))
datatable(TopSkillsGroupData)
```

#### A chart to represent Top Skill Groups
```{r}
TopSkillsGroupData <- TopSkillsGroupData %>% arrange(GroupedCount)
barplot(TopSkillsGroupData$GroupedCount, main="Top Skills by Groups", horiz=FALSE,
  names.arg=TopSkillsGroupData$Group, las=1, cex.axis = 0.5, cex.names=0.5)

```


### Some Analytical questions


### Which cities values the Programming most for Data Scientists?

```{r}
TopSkillsGroupData1 <- inner_join(ConsData, SkillGroups, by=c("skill" = "Skill"))
TopSkillsGroupDataProgByLocation <- TopSkillsGroupData1 %>% filter(Group=="Programming") %>% group_by(location) %>% summarise(Count=sum(count)) %>% arrange(desc(Count))
datatable(TopSkillsGroupDataProgByLocation)

```


### If I am a programmer, what is the next best skill I can learn?
```{r}
TopSkillsGroupData2 <- inner_join(ConsData, SkillGroups, by=c("skill" = "Skill"))
TopSkillsGroupData2 <- TopSkillsGroupData2 %>% filter(Group!="Programming")
TopNonProgSkills <- TopSkillsGroupData2 %>% group_by(skill) %>% summarise(Count=sum(count)) %>% arrange(desc(Count))
datatable(TopNonProgSkills)

```

### NY vs SF vs London Comparison for Top 4 skills
```{r}

aggDataLocNY <- ConsData %>% filter(location == "New York, NY")
aggDataLocNY <- aggDataLocNY %>% group_by(skill) %>% summarise(totalCount=sum(count))
aggDataLocNY <- aggDataLocNY  %>% arrange(desc(totalCount))
aggDataLocNY <- head(aggDataLocNY, 4)

aggDataLocSF <- ConsData %>% filter(location == "San Francisco, CA")
aggDataLocSF <- aggDataLocSF %>% group_by(skill) %>% summarise(totalCount=sum(count))
aggDataLocSF <- aggDataLocSF  %>% arrange(desc(totalCount))
aggDataLocSF <- head(aggDataLocSF, 4)

aggDataLocLdn <- ConsData %>% filter(location == "London")
aggDataLocLdn <- aggDataLocLdn %>% group_by(skill) %>% summarise(totalCount=sum(count))
aggDataLocLdn <- aggDataLocLdn  %>% arrange(desc(totalCount))
aggDataLocLdn <- head(aggDataLocLdn, 4)

ggplot() + 
geom_bar(data=aggDataLocNY, aes(x=skill, y=totalCount, fill='#999999'), stat = "identity") + 
geom_bar(data=aggDataLocSF, aes(x=skill, y=totalCount, fill='#E69F00'), stat = "identity") +
geom_bar(data=aggDataLocLdn, aes(x=skill, y=totalCount, fill='#A69F55'), stat = "identity") 
#+ scale_fill_manual(values=c("#999999", "#E69F00"), labels=c("NY", "SF"))


```