---
title: "Seekanalysis"
author: "jim lung"
date: "03-26-2017"
output: html_document
---

This part is the analysis what is the most important skills requried for data scientists at Austrialia.

Using the code from: https://www.seek.com.au/

```{r}
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
library(plotly)

australiajob <- read.csv("https://raw.githubusercontent.com/DATA607/Project3/master/seekJobs.csv")
glimpse(australiajob)

```


# Aggregation

# What is the most important skills required for data Scientists?
```{r }

unique(australiajob$Skill)
unique(australiajob$Count)
audf <- aggregate(australiajob$Count, list(australiajob$Skill), sum)
colnames(audf)<- c("Skills","TotalNumber")

audftop<-arrange(audf, desc(TotalNumber))
audftop<-audftop[2:len,]
audftop<-arrange(audftop, desc(TotalNumber))
audftop
```

# What is the most total number of skills in jobs description?
```{r }
names <- audftop$Skills
barplot(audftop$TotalNumber,main="Total number of skills", horiz=TRUE, names.arg=names, las=1, cex.axis=0.5, cex.names = 0.5)
# Top three of skills are "team", "SQL" and "Python".
```

```{r }
audftop3<-audftop[1:3,]

ggplot() +
geom_bar(data=audftop3, aes(x=Skills, y=audftop3$TotalNumber, fill='Skills'), stat = "identity")

```


# Which cities have most number of jobs for data scientist in Australia?
```{r }

audflo <- aggregate(australiajob$Count, list(australiajob$location), sum)
colnames(audflo)<- c("Location","TotalNumber")
audflo<-arrange(audflo, desc(TotalNumber))
audflo
# Most number of jobs is located at Sydney of Australia
```

# Where have the most total number of jobs for data scientists in Australia?
```{r }
names <- audflo$Location
barplot(audflo$TotalNumber,main="Location for number of jobs", horiz=TRUE, names.arg=names, las=1, cex.axis=0.5, cex.names = 0.5)

```

```{r }
ggplot() +
geom_bar(data=audflo, aes(x=Location, y=TotalNumber, fill='Location'), stat = "identity")

```



Result:
1. Top three of skills required for data scientists are "analysis", "team" and "SQL"

2. Most number of jobs is located at Sydney of Australia.


